\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage[left=1.5cm,top=1.5cm,right=1.5cm,bottom=1.5cm]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{needspace}

\setlength{\parindent}{0pt}

\begin{document}

% =========================
% HEADER (ATS friendly)
% =========================
\begin{center}
    {\Large \textbf{Martín Alejandro Grellet}}\\[-2pt]
    Tucumán, Argentina · martin.alejandro.grellet@gmail.com · +54 381 607 3574 ·
    \href{https://www.linkedin.com/in/mgrellet}{linkedin.com/in/mgrellet}
\end{center}

\vspace{6pt}

% =========================
% PROFESSIONAL SUMMARY
% =========================
{\large \textbf{PROFESSIONAL SUMMARY}}\\[4pt]
\hrule

Software Engineer with 13+ years of experience working on scalable, high-performance systems and distributed architectures. Background in Java (Spring Boot, Java 8–17) and microservices. Experience in system migrations, performance improvements, and team collaboration. Worked on systems handling high-volume transactional workloads and distributed data processing.

\vspace{10pt}

% =========================
% PROFESSIONAL EXPERIENCE
% =========================
{\large \textbf{PROFESSIONAL EXPERIENCE}}\\[4pt]
\hrule

\textbf{Siltium} \hfill Remote, Argentina\\
\textit{Software Engineer – Correo Argentino} \hfill Mar 2025 -- Present

\begin{itemize}[leftmargin=12pt]
    \item Developing a centralized Node.js/TypeScript (NestJS) application to register and manage international shipment data, improving end-to-end traceability and reducing manual processing workload by $\sim$40\%.
\end{itemize}

\textbf{AYI Group} \hfill Remote, Argentina\\
\textit{Full Stack Software Engineer} \hfill Jul 2024 -- Jan 2025

\begin{itemize}[leftmargin=12pt]
    \item Led the architectural migration from a legacy monolith to microservices (Java/Spring Boot) and microfrontends (React), improving system scalability and reducing deployment risk.
    \item Optimized MySQL query plans and indexing strategies, cutting average database response times by $\sim$35\% under peak load.
\end{itemize}

\textbf{Sovos} \hfill Tucumán, Argentina\\
\textit{Software Engineer} \hfill Aug 2022 -- Jul 2024

\begin{itemize}[leftmargin=12pt]
    \item Built a tax compliance engine for POS systems in Java/Spring Boot, enabling accurate multi-jurisdiction tax calculations used across hundreds of retail clients.
    \item Implemented and maintained CI/CD pipelines with Azure DevOps and Jenkins, reducing release cycle time and increasing deployment reliability.
    \item Refactored Java microservices (Spring Boot, Java 11/17) for performance optimization, achieving measurable throughput improvements under high-concurrency scenarios.
\end{itemize}

\textbf{Globant} \hfill Tucumán, Argentina\\
\textit{Java Software Designer – JP Morgan Chase} \hfill Mar 2022 -- Aug 2022

\begin{itemize}[leftmargin=12pt]
    \item Improved Maven dependency management and remediated security vulnerabilities flagged by Veracode static analysis, reducing critical CVE exposure.
    \item Performed testing, packaging, and deployment of Spring Boot microservices in a regulated banking environment.
\end{itemize}

\textbf{Mercado Libre} \hfill Remote, Argentina\\
\textit{Software Engineer} \hfill Sep 2021 -- Mar 2022

\begin{itemize}[leftmargin=12pt]
    \item Developed high-throughput Go-based REST APIs for payment and financial services, handling millions of daily transactions with strict SLA and regulatory compliance.
    \item Improved observability and reliability through monitoring, alerting, and production metrics analysis.
\end{itemize}

% Avoid the Sovos (Tech Lead) heading alone at the bottom of a page; move the block if needed.
\Needspace{9\baselineskip}

\textbf{Sovos} \hfill Tucumán, Argentina\\
\textit{Software Engineer / Tech Lead} \hfill Feb 2016 -- Sep 2021

\begin{itemize}[leftmargin=12pt]
    \item Led cross-functional teams of 4–6 engineers, driving technical decisions, mentoring, and improving delivery predictability.
    \item Architected and built tax-calculation microservices using Java/Spring Boot and RabbitMQ, ensuring high availability and fault tolerance in distributed environments.
    \item Led a Snowflake--Kafka proof of concept to evaluate real-time data integration, improving processing throughput by $\sim$50\% in testing.
    \item Designed POS system frontend components with AngularJS (legacy) and Java 8, supporting rollout to enterprise retail clients.
    \item Established CI/CD pipelines with Jenkins, standardizing the release process across multiple teams.
\end{itemize}

\textbf{Hewlett-Packard} \hfill Córdoba, Argentina\\
\textit{Application Support Engineer} \hfill Apr 2014 -- Feb 2016

\begin{itemize}[leftmargin=12pt]
    \item Maintained and supported SOAP/REST Web Services for mission-critical airline reservation applications.
    \item Provided 24/7 on-call production and UAT support, meeting strict SLA requirements for global airline customers.
\end{itemize}

\textbf{Globant} \hfill Tucumán, Argentina\\
\textit{Java Software Developer} \hfill May 2013 -- Apr 2014

\begin{itemize}[leftmargin=12pt]
    \item Built an internal travel portal using Java 7, Spring 3, Hibernate/JPA, and Thymeleaf/jQuery from scratch.
\end{itemize}

\textit{Earlier Experience (2010--2013):} PHP Developer at La Gaceta · Developer at Everis for Movistar Argentina · Developer at Hewlett-Packard · Developer/QA at Everis

\vspace{10pt}

% =========================
% EDUCATION
% =========================
{\large \textbf{EDUCATION}}\\[4pt]
\hrule

\textbf{Universidad del Norte Santo Tomás de Aquino} \hfill Tucumán, Argentina\\
Bachelor's Degree in Computer Engineering \hfill Graduated 2010

\vspace{10pt}

% =========================
% CERTIFICATIONS
% =========================
{\large \textbf{CERTIFICATIONS}}\\[4pt]
\hrule

\textbf{Oracle Certified Associate, Java SE 7 Programmer (1Z0-803)} \hfill 2014

\vspace{10pt}

% =========================
% SKILLS
% =========================
{\large \textbf{TECHNICAL SKILLS}}\\[4pt]
\hrule

\textbf{Core technologies:} Java (8, 11, 17), Spring Boot, Spring MVC, Hibernate/JPA, Node.js (NestJS), TypeORM, Go, TypeScript, JavaScript, SQL, Shell, React, AngularJS (legacy) \\
\textbf{Databases:} MySQL, PostgreSQL, SQL Server, Oracle, Snowflake \\
\textbf{Messaging:} Kafka, RabbitMQ \\
\textbf{DevOps \& Tools:} Docker, Jenkins, Azure DevOps, Git, Maven, Gradle \\
\textbf{Testing:} JUnit, Mockito, Integration Testing \\
\textbf{Practices:} Microservices, REST APIs, CI/CD, DDD, SOLID, Agile/Scrum

\vspace{10pt}

% =========================
% LANGUAGES
% =========================
{\large \textbf{LANGUAGES}}\\[4pt]
\hrule

\textbf{English} (Professional Working Proficiency) \quad \textbf{Spanish} (Native)

\end{document}